Automatic Identification and Annotation of Tasks in Structured Programs

### 2018-04-04 docs/ACM/paper.tex
Removing repeated reference to Antao's work.

Annotation systems have risen to a place of prominence as a simple and
effective means to write parallel programs.
Examples of such systems include OpenMP~\cite{JaegerCP15},
OpenACC~\cite{OpenACC20}, OpenHMPP~\cite{Andion14}, OpenMPC~\cite{Lee10},
OpenSs~\cite{MeenderinckJ11}, Cilk++~\cite{Leiserson09} and
Tareador~\cite{Ayguade15}.
Annotations work as a meta-language: they let developers grant parallel
semantics to syntax originally written to execute sequentially.
%\guido{What do you mean by modern accelerators? Not clear.}
Combined with modern hardware accelerators such as GPUs and FPGAs, they have led
to substantial performance gains~\cite{Bertolli14,Martineau16,Mendonca17,Poesia17,Reyes12,Samuel16,Wienke12}.
%\guido{Suppport what?}
Nevertheless, although convenient, the use of annotations is not straightforward, 
and still lacks supporting tools that help programmers to check if annotations
are correct and/or effective.
%replaced:
%Yet, even if convenient,

@@

We have implemented all the techniques described in this paper in
LLVM~\cite{Lattner04}.
This decision was motivated by two factors.
First, the possibility to reuse all the infra-structure already
available in LLVM to infer symbolic bounds of integer
expressions~\cite{Mendonca17}.
Second, the state-of-the-art support that LLVM already provides to the
compilation of OpenMP~\cite{Antao16,Bertolli14,Martineau16,Samuel16}.
In this section, we evaluate this implementation, focusing on four research
questions:
%
\begin{compactitem}
\item \textsf{[Performance]}: how do our automatically annotated programs
compare against their sequential counterparts, or against manually annotated
versions?
\item \textsf{[Optimizations]}: what is the impact of the cost model
(Section~\ref{sub:profit}) and recursion bounding (Section~\ref{sub:ir}) onto
the programs that we annotate?
\item \textsf{[Versatility]}: how effective is \Taskminer{} in finding
opportunities to annotate general benchmarks?
\item \textsf{[Scalability]}: what is the runtime complexity of our
implementation of \Taskminer?
\end{compactitem}

>>>>

Annotation systems have risen to a place of prominence as a simple and
effective means to write parallel programs.
Examples of such systems include OpenMP~\cite{JaegerCP15},
OpenACC~\cite{OpenACC20}, OpenHMPP~\cite{Andion14}, OpenMPC~\cite{Lee10},
OpenSs~\cite{MeenderinckJ11}, Cilk++~\cite{Leiserson09} and
Tareador~\cite{Ayguade15}.
Annotations work as a meta-language: they let developers grant parallel
semantics to syntax originally written to execute sequentially.
%\guido{What do you mean by modern accelerators? Not clear.}
Combined with modern hardware accelerators such as GPUs and FPGAs, they have led
to substantial performance gains~\cite{Bertolli14,Martineau16,Mendonca17,Poesia17,Reyes12,Antao16,Wienke12}.
%\guido{Suppport what?}
Nevertheless, although convenient, the use of annotations is not straightforward, 
and still lacks supporting tools that help programmers to check if annotations
are correct and/or effective.
%replaced:
%Yet, even if convenient,

@@

We have implemented all the techniques described in this paper in
LLVM~\cite{Lattner04}.
This decision was motivated by two factors.
First, the possibility to reuse all the infra-structure already
available in LLVM to infer symbolic bounds of integer
expressions~\cite{Mendonca17}.
Second, the state-of-the-art support that LLVM already provides to the
compilation of OpenMP~\cite{Antao16,Bertolli14,Martineau16}.
In this section, we evaluate this implementation, focusing on four research
questions:
%
\begin{compactitem}
\item \textsf{[Performance]}: how do our automatically annotated programs
compare against their sequential counterparts, or against manually annotated
versions?
\item \textsf{[Optimizations]}: what is the impact of the cost model
(Section~\ref{sub:profit}) and recursion bounding (Section~\ref{sub:ir}) onto
the programs that we annotate?
\item \textsf{[Versatility]}: how effective is \Taskminer{} in finding
opportunities to annotate general benchmarks?
\item \textsf{[Scalability]}: what is the runtime complexity of our
implementation of \Taskminer?
\end{compactitem}
